OSF management

### 2020-12-31 osf/manage-osf.Rmd
:bug: - use xfun::Rscript_call() to knit all READMEs

We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting) by running `osf/knit-all.R`.

------
**NOTE**

For some reason I can't get this file to knit the other Rmd files when knitted (I get an error).
So for now we need to manually run the `osf/knit-all.R` script before uploading files to OSF.
I asked on StackOverflow how to fix this: <https://stackoverflow.com/q/65505119/2804314>.

------

@@

tgs <- data_comp_files %>% filter(name == "TextGrids")
osf_upload(tgs, path = "./osf/comps/dataset/textgrids/README.md", conflicts = "overwrite", verbose = T)
```

>>>>

We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting).

```{r knit-all, message=FALSE, warning=FALSE}
files <- list.files("./osf/comps", pattern = "[.]Rmd$", recursive = T, full.names = T)

for (f in files) {
  xfun::Rscript_call(rmarkdown::render, list(f))
}
```

@@

tgs <- data_comp_files %>% filter(name == "TextGrids")
osf_upload(tgs, path = "./osf/comps/dataset/textgrids/README.md", conflicts = "overwrite", verbose = T)

osf_rm(osf_ls_files(data_comp, "Materials/Norming results", pattern = "README.md"), check = FALSE)
osf_upload(osf_ls_files(data_comp, "Materials", type = "folder", pattern = "Norm"), path = "./osf/comps/dataset/materials/norming-results/README.md", conflicts = "overwrite", verbose = T)

osf_rm(osf_ls_files(data_comp, "Materials/Trial lists", pattern = "README.md"), check = FALSE)
osf_upload(osf_ls_files(data_comp, "Materials", type = "folder", pattern = "Trial lists"), path = "./osf/comps/dataset/materials/trials/README.md", conflicts = "overwrite", verbose = T)
```
